




<====================< Nots with Tree >====================>
1) Definition => is a hierarchical tree structure with [ root value | subtrees of children ]

2) Components => [Node | Root | Child | Parent | Leaf | Subtree | Height | Depth]
   1. Node => individual element of a tree, contains [ Data | References => (rite | left)  ]

   2. Root => this would be the starting point, It has no parent node.

   3. Child => node connected to another nodes called a child, 
               The node it connects to is called its parent.

   4. Parent => node that has one or more children.

   5. Leaf => node with no children is called a leaf or terminal node,
              It is at the end of a path in the tree.

   6. Subtree => is a portion of a tree that includes a node and all of its descendants.

   7. Height => is length of the longest path from the root to a leaf,

   8. Depth => is number of edges from the root to that node.

3) Operations on Trees => [ Insertion | Deletion | Searching | Height Calculation | 
                            Finding Minimum and Maximum Values | Balancing | Merging Trees
                            Traversal => ( In-order | Pre-order | Post-order | Level-order ) ]

4) Types of Trees => 

   1. (Binary Tree) -> Each node has at most two children,
                     referred to as the left child and the right child.

       use case -> expression parsing, hierarchical data representation,

   2. (Binary Search Tree (BST)) -> where the left child contains only nodes with values less than the parent node,
                                    the right child contains only nodes with values greater than the parent node.

        use case -> searching, insertion, deletion operations,

   3. (Balanced Trees) -> A tree structure where the height difference
                          between the left and right subtrees of any node is bounded.

        //|\\

   4. (Heap)
   
   5. (Trie (Prefix Tree))

   6. (B-Tree)

   7. (N-ary Tree)

   8. (Segment Tree)

   9. (Suffix Tree)

   10. (Fenwick Tree (Binary Indexed Tree))

5) implementation of Operations with c++,
   1. Insertion => 
      1.1. 

   




